Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-09-27 saner/paper.tex
Updates from Overleaf

\documentclass[sigconf,review, table]{acmart}

@@

\setcopyright{acmcopyright}
\copyrightyear{2019}
\acmYear{2019}
\acmDOI{10.1145/1122445.1122456}
\acmMonth{8}

\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}

@@

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use. We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
\end{abstract}

\keywords{code clones, refactoring, static code analysis, object-oriented programming}

@@

\section{The CloneRefactor tool}
To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}. We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.

None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}. This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}. In the following sections, we explain these steps.
\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/flow}
  \caption{Simple flow diagram of CloneRefactor.}
  \label{fig:clonerefactorflow}
\end{figure}

@@

\subsection{Tool Validation}
We have verified the correctness of CloneRefactor through unit tests and empirical verification.\todo{With unit test you are testing the properties which is verification. With projects you are validating as you are checking whether its finding what is it supposed to be finding.} First, we created a set of 57 control projects to verify the correctness in many (edge) cases. These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified. Next, we run the tool over the corpus and manually verify samples of the acquired results. This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.

@@

\section*{Acknowledgments}
We would like to thank the Software Improvement Group for their continuous support in this project. In particular, we would like to thank Xander Schrijen for his invaluable input in this research. Furthermore, we would like to thank Sander Meester for his proofreading efforts and feedback.

>>>>

\documentclass[10pt,conference]{IEEEtran}

@@

@@

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or returns data and the amount of external data that cloned fragments use. We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
\end{abstract}

\begin{IEEEkeywords}
code clones, refactoring, static code analysis, object-oriented programming
\end{IEEEkeywords}

@@

\section{The CloneRefactor tool}
To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}. We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.

None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor. This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}. In the following sections, we explain these steps.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/flow}
  \caption{Simple flow diagram of CloneRefactor.}
  \label{fig:clonerefactorflow}
\end{figure}

@@

\subsection{Tool Validation}
We have validated the correctness of CloneRefactor through unit tests and empirical validation. First, we created a set of 57 control projects to verify the correctness in many (edge) cases. These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified. Next, we run the tool over the corpus and manually verify samples of the acquired results. This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.

@@
